## Evolutionary History of the Main Biological Characters of Siphonophores

### 2017-02-12 character_coding/CharacterEvolution.Rmd
added more simmaps

@@

```{r, echo=F}
#Simmap SEX
plotTree(ultratree, lwd = 4)
make.simmap(ultratree, sex, nsim = 100) -> sex_sim
sex_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Dioeicous", "Monoeicous")
nodelabels(pie=(describe.simmap(sex_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(sex_sim)

@@

>>>>

```{r, include=F}
#Make simmap objects
make.simmap(ultratree, sex, nsim = 100) -> sex_sim

@@

```{r, echo=F}
#Simmap SEX
plotTree(ultratree, lwd = 4)
sex_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Dioeicous", "Monoeicous")
nodelabels(pie=(describe.simmap(sex_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(sex_sim)

@@

###Presence of palpons:
```{r, echo=F}
#Simmap PALPONS
plotTree(ultratree, lwd = 4)
make.simmap(ultratree, palpons, nsim = 100) -> palpons_sim
palpons_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
nodelabels(pie=(describe.simmap(palpons_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(palpons_sim)
```

###Presence of tentilla:
```{r, echo=F}
#Simmap TENTILLA
plotTree(ultratree, lwd = 4)
make.simmap(ultratree, tentilla, nsim = 100) -> tentilla_sim
tentilla_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
nodelabels(pie=(describe.simmap(tentilla_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(tentilla_sim)
```

###Presence of Nectophores:
```{r, echo=F}

###Position of Nectosome:
```{r, echo=F}

###Nectophore number and types:

###Presence of Pneumatophore:
```{r, echo=F}

###Ocean Depth Zone:
```{r, echo=F}
